### 2014-12-13 paper.tex
Add a paragraph to the standards for gerrymandering and mess with the organization

  \subsection{Relationship Between Compactness and Bias Measures}

  %TODO: write this section

  \section{Legislative and Legal Changes}

>>>>

  \subsection{Standards for Gerrymandering}

  Taken together, efficiency gap and compactness can give a very strong indication of gerrymandering.  If a state has noncompact districts, this suggests that the districts may have been drawn unfairly; partisan bias can confirm the particular type of advantage they give.  Conversely, high partisan bias might be justifiable if a districting plan is compact, on the basis that the political geography naturally benefits one side, as Chen and Rodden suggest.~\cite{chenrodden}  In addition, this relationship gives a framework for evaluating compactness metrics and other metrics of gerrymandering: if a metric tends to correlate with the other existing metrics of gerrymandering, it can be used as an additional indicator.
